Staged Abstract Interpreters

### 2018-11-17 paper/50_cases.tex
interval
revise paper

\begin{lstlisting}
case class Interval(lb: Rep[Double], ub: Rep[Double]) {
  def +(that: Interval): Interval = that match {
    case Interval(lb_, ub_) => Interval(lb + lb_, ub + ub_)
  }
  def -(that: Interval): Interval = that match {
    case Interval(lb_, ub_) => Interval(lb - lb_, ub_ - ub) 
  }
  ...
}
\end{lstlisting}

>>>>

Interval domain is a relative simple domain which consists of two numeric fields, an upper bound 
and a lower bound. Here we annotate the upper bound and lower bound fields to be of type @Rep[Double]@.
The operations such as @+@ of two intervals produce a new

\begin{lstlisting}
case class Interval(lb: Rep[Double], ub: Rep[Double]) {
  def +(that: Interval): Interval = that match {
    case Interval(lb_, ub_) => Interval(lb + lb_, ub + ub_)
  }
  ...
}
\end{lstlisting}

### 2018-11-17 paper/60_eval.tex
revise paper

To evaluate the performance can be improved through staging, we use the abstract
interpreter demonstrated in the paper to analyze some Scheme programs. We implement
a desugaring transformation for a large subset of scheme that transforms into the
small language we used in the paper.
We use the same generic interface with a 0-CFA-like abstraction, and the unstage abstract
interpreter forms the baseline.

@@

@@

%on a suite of benchmark scheme programs that are also used in \cite{Johnson:2013:OAA:2500365.2500604, ashley:practical}. 
We used the following benchmark programs:
\begin{itemize}
    \item \textbf{fib:} a program that recursively calculates the $n$-th fibonacci number in
        exponential time.
    \item \textbf{church:} a program introduced by \todo{cite Dimitrios Vardoulakis and Olin Shivers. CFA2: a Context-Free approach
        to Control-Flow analysis. Logical Methods in Computer Science,
        7(2), 2011.} to test distributivity of multiplication for numbers in Church Encoding \todo{ cite }
\end{itemize}

@@

Our evaluations have shown that the staged abstract interpreter performs well in general.
Particularly in some interesting cases that are considered to be the worst case scenario
in the control-flow analysis, the staged version outperforms the unstaged abstract 
interpreter by a wide margin.

However, there also exists some programs where the unstaged abstract interpreter yields 
results faster than the unstaged interpreter.

>>>>

To evaluate the performance can be improved through staging, we use the abstract
interpreter demonstrated in the paper to analyze some Scheme programs. We first implement
a desugaring transformation for a large subset of scheme that transforms into the
small language we used in the paper.
We use the same generic interface with a 0-CFA-like abstraction, and the unstage abstract
interpreter forms the baseline.

@@

Our evaluations have shown that the staged abstract interpreter performs well in some
interesting cases that are considered to be the worst case scenario in the control flow
analysis, the staged version outperforms the unstaged abstract interpreter by a wide
margin (up to 3x performance gain).

@@

%on a suite of benchmark scheme programs that are also used in \cite{Johnson:2013:OAA:2500365.2500604, ashley:practical}. 
We used the following benchmark programs:
\begin{itemize}
    \item \textbf{fib:} a program that recursively calculates the $n$-th fibonacci number in
        exponential time.
    \item \textbf{church:} a program introduced by \todo{cite Dimitrios Vardoulakis and Olin Shivers. CFA2: a Context-Free approach
        to Control-Flow analysis. Logical Methods in Computer Science,
        7(2), 2011.} to test distributivity of multiplication for numbers in Church Encoding \todo{ cite }
    \item \textbf{kcfa3/kcfa-worst-case-n:} Benchmark programs that are supposed to
      be tough cases for CFA.
    \item \textbf{fermat:} Fermat and Solovay-Strassen primality testing in Scheme by
      Matthew Might.
    \item \textbf{rsa:} The RSA public key encryption algorithm in Scheme.
\end{itemize}

@@

\begin{figure}[h]
\begin{tabular}{@{}llll@{}}
\toprule
    Program            & unstaged   & staged     & $\Delta$ of median \\ \midrule
    fib                & 1.020      & 2.046      & -50.14\%          \\
    rsa                & 35.928     & 145.306    & -75.27\%          \\
    kcfa3              & 2.934      & 5.671      & -48.27\%          \\
    church             & 884.800    & 545.736    & +62.13\%          \\
    fermat             & 15.673     & 68.790     & -77.22\%          \\
    kcfa-worst-16      & 320.689    & 301.564    & +6.34\%           \\
    kcfa-worst-32      & 3,685.615  & 1,854.461  & +98.74\%          \\
    kcfa-worst-64      & 49,422.666 & 14,849.725 & +232.82\%         \\
    \bottomrule
\end{tabular}
\caption{Evaluation result.} \label{evaluation_result}
\end{figure}

Figure~\ref{evaluation_result} shows the benchmark evaluation results. The "unstaged" and "staged" columns
show the median time to finish the abstract interpretation (in milliseconds). The "$\Delta_{median}$"
column shows the performance change from the unstaged abstract interpreter to the staged version.\\

However, there also exists some programs where the unstaged abstract interpreter yields 
results faster than the unstaged interpreter.
From the data shown above, we observed that 
However, in general, the unstaged abstract interpreter yields results faster
than the unstaged interpreter.
